gilmore-nysds-2016

### 2016-08-12 nysds-2016/gilmore-nysds-2016.Rmd
More tweaks

>- Video record all tasks, measures, and behaviors
>- Share the recordings openly with other researchers
>- Share all questionnaires, tasks, displays
>- Share statistical, computational, data workflows
>- Prepare to share from the beginning
>- Seek permission to share data from participants

@@

>>>>

>- Video record all tasks, measures, and behaviors
>- Share the recordings openly with other researchers

## *Journal of Visualized Experiments*

<iframe src="http://www.jove.com/" width=750px height=500px>
</iframe>

## But, a reproducible behavioral science must *also*...

>- Share all questionnaires, tasks, displays
>- Share statistical, computational, data workflows
>- Prepare to share from the beginning
>- Seek permission to share data from participants

## [Databrary.org](http://databrary.org)

@@

## Databrary's structure

- Datasets have own page; shared datasets have DOIs.
- Data about testing *sessions* (locations, dates/times, people) stored in *spreadsheet*
- Session data organized in *timeline*
- Store data AND materials (displays, protocols, etc.)
